\documentclass[../main.tex]{subfiles}
\begin{document}

In the context of the rapidly growing beauty industry, the demand for virtually trying on new hairstyles realistically before committing to an actual haircut is becoming essential to minimize risks for both customers and salons. Historically, altering hairstyles in images relied heavily on manual post-processing or rudimentary deep learning models, which often failed to maintain the natural integrity of human facial biology and lighting structures.

In this report, we propose and construct a "Virtual Hairstyle Try-On" (TryHairStyle) system based on the state-of-the-art Stable Diffusion XL (SDXL) Inpainting architecture. The system distinguishes itself through a continuous Dual-Conditioning mechanism, integrating the hairstyle style-transfer capabilities of IP-Adapter Plus with the absolute identity-preservation power of InstantID. The visual processing pipeline is further fortified by the semantic segmentation Transformer network (SegFormer) for automated dynamic hair masking, coupled with three-dimensional facial orientation alignment via 3DDFA\_V2 mesh configurations.

Experimental outcomes demonstrate the system's innovative capability to not only comprehensively transfer complex elements—such as parting lines, curl structures, and hair volume from reference images—but also to meticulously retain the original user's identity, preserving facial contours, eye gaze, lighting, and background untouched. Furthermore, our fine-tuning modifications on the U-Net LoRA network, driven by Edge-weighted Mask-Aware Loss strategy, empower the algorithm to achieve extreme precision along thin hair boundaries. This engineering process yields a fully functional end-to-end software solution, paving the way for practical commercial applications in the digital beauty and retail hair industry.

\end{document}
